\LARGE \bf Planning with Attitude

### 2020-10-09 paper/main.tex
Update timing results and plots

% Plotting
\usepackage{pgfplots}
\pgfplotsset{compat=1.15,
	legend style={font=\footnotesize},
}
\usepackage{tikzscale}

@@

    \subsection{Results}

@@

@@

        \subsubsection{Quadrotor Flip}
	    Similar to the previous example, we use a set of waypoints to encourage the
	    quadrotor to do a flip. The cost weights for this example were
	    \begin{align*}
	        Q_\text{nom} &= \text{diag}(10^{-2},10^{-2},5 \!\times\! 10^{-2}, 10^{-3} I_3,
    	        10^{-3} I_3, 10^{-2} I_3) \\
	        Q_w &= \text{diag}(10^3, 10, 10^3, 5000 I_3, I_3, 10 I_3) \\
	        Q_N &= \text{diag}(10 I_3, 100 I_3, 10 I_6)  
	    \end{align*}
	    Four intermediary knotpoints were used to encourage the quadrotor to be at angles
	    of \ang{90}, \ang{180}, \ang{270}, and \ang{360}. The quadrotor was constrained
	    to stay above the floor and move to a goal state 2 meters away in the $+y$
	    direction. The solver is initialized with a dynamically infeasible trajectory
	    that linearly interpolates between the initial and final states, rotating the
	    quad around the x-axis a full \ang{360}.

	    Figure \ref{fig:quad_flip} shows snapshots of the trajectory as generated using
	    iMLQR within the ALTRO solver to handle constraints. The trajectory generated by
	    iLQR with quaternions and quadratic costs was successful but had a slightly
        different trajectory. iLQR with Euler angles failed to solve the problem.

            \begin{figure}[t]
                \centering
                \includegraphics[height=5.2cm,trim={0 3cm 0 0},clip]{figures/quad_flip.png}
                \caption{Snapshots of the quadrotor flip trajectory. The
                    red-colored quadrotors represent the state near t=0 s and the
                    green-colored quadrotors represent the state near t=5.0 s
                }
                \label{fig:quad_flip}
            \end{figure}

@@

        \begin{figure}[h]
            \centering
            \includegraphics[height=3.5cm]{figures/barrellroll.png}
            \caption{Barrel roll trajectory computed by iterative MLQR using a terminal cost to encourage an upside-down attitude.}
            \label{fig:barrellroll}
        \end{figure}

>>>>

% Plotting
\usepackage{pgfplots}
\pgfplotsset{compat=1.15,
	legend style={font=\footnotesize},
}
\usepackage{tikzscale}
% \pgfplotsset{every axis plot post/.style={
%     very thick,
% }
% }

@@

    \subsection{Results}
    \begin{figure}
        \centering
        \includegraphics[width=\columnwidth, height=5cm]{figures/wahba_convergence.tikz}
        \caption{Convergence comparison for Wahbas problem. By performing Newton's method
        on the error quaternion and applying the result to the full quaternion we achieve
        quadratic convergence, whereas the more na\"ive approach doesn't converge to zero
        error.}
    \end{figure}

@@

    \begin{table}
        \centering
        \input{figures/timing_results.tex}
        \label{tab:timing_results}
        \caption{Trajectory Optimization Timing Results}
    \end{table}

@@

        \subsection{Satellite Attitude Keep-Out}
        \begin{figure}
            \centering
            \includegraphics{figures/kevins_plots/attitude_slew_plot.tikz}
            \caption{Attitude keep out}
        \end{figure}

@@

        \begin{figure}[h]
            \centering
            \includegraphics[width=\columnwidth]{figures/barrellroll.png}
            \caption{Barrel roll trajectory computed by iterative MLQR using a terminal cost to encourage an upside-down attitude.}
            \label{fig:barrellroll}
        \end{figure}

        \begin{figure}[h]
            \centering
            \includegraphics[height=4cm,width=\columnwidth]{figures/c_max_convergence.tikz}
            \caption{Constraint convergence when solving the barrell roll problem. Compares 
            the convergence of the original version of ALTRO versus the new, modified version
            that optimizing on the error state.}
            \label{fig:c_max_convergence}
        \end{figure}

        \subsubsection{Quadrotor Flip}
        We sucessfully optimized a 360 degree flip trajectory for a quadrotor using the 
        modified version of ALTRO.
	    Four intermediary knotpoints were used to encourage the quadrotor to be at angles
	    of \ang{90}, \ang{180}, \ang{270}, and \ang{360}. The quadrotor was constrained
	    to stay above the floor and move to a goal state 2 meters away in the $+y$
	    direction. The solver is initialized with a dynamically infeasible trajectory
	    that linearly interpolates between the initial and final states, rotating the
	    quad around the x-axis a full \ang{360}.

	    Figure \ref{fig:quad_flip} shows snapshots of the trajectory as generated using
	    ALTRO.  t

            \begin{figure}[t]
                \centering
                \includegraphics[height=5.2cm,trim={0 0cm 0 0},clip]{figures/quadflip.png}
                \caption{Snapshots of the quadrotor flip trajectory. The
                    red-colored quadrotors represent the state near t=0 s and the
                    green-colored quadrotors represent the state near t=5.0 s
                }
                \label{fig:quad_flip}
            \end{figure}
